An enhancer code compendium of early human neural and neural crest development

### 2025-04-25 manuscript.tex
Data and code

>>>>

Raw sequencing data, scATAC-seq fragment files, scRNA-seq count matrix, cell metadata, consensus peaks, and cell- and 
region topic probabilities for the human neural tube organoids are available on Gene Expression Omnibus (GEO) using 
accession number \href{https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE295337}{GSE295337}
(reviewer token: ). %TODO: add before submission.
Raw sequencing data of the human embryo are available through the European Genome Phenome Archive 
(). %TODO: Add link to EGA
scATAC-seq fragment files, scRNA-seq count matrix, cell metadata, consensus peaks and cell-and region topic
probabilities of the human embryos are available through Zenodo (). %TODO: upload embryo data to Zenodo and provide link.
$DeepNeuralTube_O$ and $DeepNeuralTube_E$ are available via Zenodo (). %TODO: upload models to Zenodo and provide link.
Data can be interactively explored using the \href{https://scope.aertslab.org/#/Neural_Tube/*/welcome}{neural tube SCope session} and on the \href{}{UCSC genome browser} %TODO: build genome browser track hub.
The enhancer compendium generated in this study is available at something.aertslab.org. %TODO: generate landing page

Code to reproduce all figures in this manuscript as well as a full history of the manuscript itself is available 
through GitHub: \href{https://github.com/SeppeDeWinter/DeWinter_NeuralTube}{SeppeDeWinter/DeWinter\_NeuralTube}.
